\begin{enumerate}[label=\thesubsection.\arabic*.,ref=\thesubsection.\theenumi]
\item $ABCD$ is a trapezium in which $AB  \parallel  DC$ and its diagonals intersect each other at the point $O$. Show
that
$\frac{AO}{ BO}=\frac{CO}{  DO}$
\item In an isosceles $\triangle ABC$, with $AB = AC$, the bisectors of $\angle B$ and $\angle C$ intersect each other at $O$. Join $A$ to $O$. Show that :
\begin{enumerate} 
\item $OB = OC$ 
\item $AO$ bisects $\angle A$
\end{enumerate}
\item $ABC$ is an isosceles triangle in which altitudes $BE$ and $CF$ are drawn to equal sides $AC$ and $AB$ respectively . Show that these altitudes are equal.
%
\item $ABC$ is a triangle in which altitudes $BE$ and $CF$ to sides $AC$ and $AB$ are equal. Show that
%
\begin{enumerate} 
\item $\triangle  ABE \cong  \triangle  ACF $
\item  $AB = AC$, i.e., $ABC$ is an isosceles triangle.
\end{enumerate}
\item $ABCD$ is a trapezium in which $AB  \parallel  DC$ and its diagonals intersect each other at the point $O$. Show
that
$\frac{AO}{ BO}=\frac{CO}{  DO}$
%
\item  $D$ is a point on the side $BC$ of a $\triangle ABC$ such that  $\angle  ADC =  \angle  BAC$. Show that $CA^2 = CB.CD$.
%
\item $BL$ and $CM$ are medians of a $\triangle ABC$ right angled at $A$. Prove that $4 (BL^2 + CM^2
) = 5 BC^2$ .
\item $O$ is any point inside a rectangle $ABCD$. Prove that $OB^2+OD^2 = OA^2+OC^2$.
\item   $D$ is a point on side $BC$ of  $\triangle  ABC$ such that
$\frac{BD}{CD}= \frac{AB}{AC}  $.  Prove that $AD$ is the bisector of  $\angle  BAC$.
\item $\vec{Q}$ is a point on the side $\vec{SR}$ of $\triangle \vec{PSR}$ such that $\vec{PQ=PR}$. Prove that $\vec{PS>PQ}$.
\item $\vec{S}$ is any point on side $\vec{QR}$ of a $\triangle \vec{PQR}$. Show that $\vec{PQ+QR+RP>2PS}$.
\item $\vec{D}$ is any point on side $\vec{AC}$ of a $\triangle \vec{ABC}$ with $\vec{AB=AC}$. Show that $\vec{CD<BD}$.
\item $AD$ is the bisector of $\angle BAC$. Prove that $AB>BD$.
\item Prove that sum of any two sides of a triangle is greater than twice the median with respect to the third side.
\item Prove that in a triangle, other than an equilateral triangle, angle opposite the longest side is greater than $\frac{2}{3}$ of a right angle.
\item P is a point in the interior of a parallelogram $ABCD$. Show that
\begin{enumerate}
\item $ar (APB) + ar (PCD) = \frac{1}{ 2}ar (ABCD)$
\item $ar (APD) + ar (PBC) = ar (APB) + ar (PCD)$
\end{enumerate}
%
\item $PQRS$ and $ABRS$ are parallelograms and $X$ is any point on side $BR$. show that 
\begin{enumerate} 
\item $ar (PQRS) = ar (ABRS)$
\item $ar (AX S) = \frac{1}{ 2} ar (PQRS)$
\end{enumerate}
\item $ABCD$ is a quadrilateral and $BE  \parallel  AC$ and also $BE$ meets $DC$ produced at $E$. Show that area of $ \triangle  ADE$ is equal to the area of the quadrilateral $ABCD$.
%
\item $E$ is any point on median $AD$ of a  $\triangle  ABC$. Show that $ar (ABE) = ar (ACE)$.
\item  In a $\triangle ABC, E$ is the mid-point of median $AD$. Show that $ar (BED) = \frac{1}{ 4}ar(ABC)$ .
%
\item AB is a diameter of the circle, $CD$ is a chord equal to the radius of the circle. $AC$ and $BD$ when extended intersect at a point $E$. Prove that $\angle AEB = 60\degree$.
\item If the non-parallel sides of a trapezium are equal, prove that it is cyclic.
\item Prove that the line of centres of two intersecting circles subtends equal angles at the
two points of intersection.
%
\end{enumerate}
