\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
    \item A polygon of nine sides, each of length $2$, is inscribed in a circle. The radius of the circle is \dots \hfill (1987 - 2 Marks) 
    \item A circle is inscribed in a equilateral triangle of a side $a$. The area of any square inscribed in this circle is \dots \hfill (1994 - 2 Marks)  
    \item In a triangle $ABC$, $a:b:c = 4:5:6$. The ratio of the radius of the circumstances to that of the incircle is \dots \hfill (1996 - 1 Marks) 
        \item The sum of the radii of inscribed and circumscribed circles for an $n$ sided regular polygon of side $a$, is \hfill\brak{2003}
\begin{multicols}{4}
\begin{enumerate}
        \item $\frac{a}{4} \cot{\brak{\frac{\pi}{2n}}}$         
        \item $ a \cot{\brak{\frac{\pi}{n}}}$ 
        \item $\frac{a}{2} \cot{\brak{\frac{\pi}{2n}}}$ 
        \item $ a \cot{\brak{\frac{\pi}{2n}}}$
\end{enumerate}
\end{multicols}
\item For a regular polygon, let $r$ and $R$ be the radii of the inscribed and the circumscribed circles. A false statement among the following is \hfill\brak{2010}
\begin{enumerate}
        \item There is a regular polygon with $\frac{r}{R}=\frac{1}{\sqrt{2}}$                    
        \item There is a regular polygon with $\frac{r}{R}=\frac{2}{3}$ 
        \item There is a regular polygon with $\frac{r}{R}=\frac{\sqrt{3}}{2}$ 
        \item There is a regular polygon with $\frac{r}{R}=\frac{1}{2}$
\end{enumerate}
    \item Let $A_{0}A_{1}A_{2}A_{3}A_{4}A_{5}$ be a regular hexagon inscribed in a circle of unit radius. Then the product of the lengths of the line segments $A_{0}A_{1}$,$A_{0}A_{2}$ and $A_{0}A_{4}$ is 
    \hfill{(1998 - 2 mark)}
    \begin{multicols}{2}
    	\begin{enumerate}
    		\item ${\frac{3}{4}}$
    		\item $3\sqrt{3}$
    		\item $3$
    		\item ${\frac{3\sqrt{3}}{2}}$
    	\end{enumerate}
    \end{multicols}
    \item In a triangle $PQR$, $\vec{P}$ is the largest angle and $\cos{P} = \frac{1}{3}$. Further the incircle of the triangle touches the sides $PQ,QR \text{ and } RP$ at $\vec{N},\vec{L} \text{ and } \vec{M}$ respectively, such that the lengths of $PN, QL \text{ and } RM$ are consecutive even integers. Then possible length(s) of the side(s) of the triangle is(are)
    \hfill{(Jee Adv. 2013)}
    \begin{multicols}{2}
    	\begin{enumerate}
    		\item $16$
    		\item $24$
    		\item $18$
    		\item $22$
    	\end{enumerate}
    \end{multicols}
    \item In a triangle $XYZ$, let $x,y,z$ be the lengths of sides opposite to angles $\vec{X},\vec{Y},\vec{Z} \text{ and } 2s = x+y+z$. If ${\frac{s-x}{4}}={\frac{s-y}{3}}={\frac{s-z}{2}}$ and area of the incircle of the triangle $XYZ$ is ${\frac{8\pi}{3}}$
    \hfill{(Jee Adv. 2016)}
    \begin{enumerate}
    	\item area of the triangle is $6\sqrt{6}$
    	\item the radius of circumcirle of $XYZ$ is ${\frac{35\sqrt{6}}{6}}$
    	\item $sin\frac{X}{2}sin\frac{Y}{2}sin\frac{Z}{2} = \frac{4}{35}$
    	\item $sin^{2}\brak{\frac{X+Y}{2}}$ = $\frac{3}{5}$
    \end{enumerate}
    \item In a triangle $PQR$, let $\angle PQR = 30\degree$ and the sides $PQ \text{ and } QR$ have lengths $10\sqrt{3}$ and $10$ respectively. Then which of the following statements is(are) TRUE?
    \hfill{(Jee Adv. 2018)}
    \begin{enumerate}
    	\item $\angle QPR = 45\degree$
    	\item the area of the triangle $PQR$ is $25\sqrt{3}$ and $\angle QRP = 120\degree$
    	\item the radius of the incircle of triangle $PQR$ is $10\sqrt{3}-15$
    	\item the radius of circumcirle $PQR$ is $100\pi$
    \end{enumerate}
    \item In a non-right-angle triangle $\Delta PQR$, let $p,q,r$ denote the lengths of the sides opposite to the angles at $\vec{P},\vec{Q},\vec{R}$ respectively. The median from $\vec{R}$ meets the side $PQ$ at $\vec{S}$, the perpendicular from $\vec{P}$ meets the side $QR$ at $\vec{E}$, $RS \text{ and } PE$ intersect at $\vec{O}$. If $p = \sqrt{3}$, $q = 1$ and the radius of the circumcircle at $\Delta PQR$ equals $1$, then which of the following options is(are)\\ correct.
    \hfill{(Jee Adv. 2018)}
    \begin{enumerate}
    	\item Radius of incircle of $\Delta PQR$ = $\frac{\sqrt{3}}{2}\brak{2-\sqrt{3}}$
    	\item Area of $\Delta SOE = \frac{\sqrt{3}}{12}$
    	\item Length of $OE = \frac{1}{6}$
    	\item Length of $RS = \frac{\sqrt{7}}{2}$
    \end{enumerate}
\item Which of the following pieces of data does NOT uniquely determine an acute-angled triangle $\triangle ABC$ ($\vec{R}$ being the radius of the circumcircle)?
\begin{enumerate}
\item $a, \sin A, \sin B$
\item $a, b, c$
\item $a, \sin B, R$
\item $a, \sin A, R$
\end{enumerate}
\hfill (2002S)
\item One angle of an isosceles $\triangle$ is $120\degree$ and radius of its incircle $= \sqrt{3}$. Then the area of the triangle in sq. units is 
\begin{enumerate}
\item $7+12\sqrt{3}$
\item $12-7\sqrt{3}$
\item $12+7\sqrt{3}$
\item $4\pi$
\end{enumerate}
\hfill (2006 - 3M, -1)

\item Let $ABCD$ be a quadrilateral with area $18$, with side $AB$ parallel to the side $CD$ and $2AB = CD$. Let $AD$ be perpendicular to $AB$ and $CD$. If a circle is drawn inside the quadrilateral $ABCD$ touching all the sides, then the radius is
\begin{enumerate}
\item $3$
\item $2$
\item $\frac{3}{2}$
\item $1$
\end{enumerate}
\hfill (2007 - 3 Marks)

\end{enumerate}
