\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
    \item Let $ABCD$ be a convex quadrilateral with perpendicular diagonals. If $AB = 20$, $BC = 70$, and $CD = 90$, then what is the value of $DA$?\hfill(PRMO 2014)
    \item In a triangle with integer side lengths, one side is three times as long as a second side, and the length of the third side is $17$. What is the greatest possible perimeter of the triangle? \hfill(PRMO 2014)
    \item In a triangle $ABC$, $X$ and $Y$ are points on the segments $AB$ and $AC$, respectively, such that $ AX : XB = 1 : 2 $ and $ AY : YC = 2 : 1$. If the area of triangle $AXY$ is $10$, then what is the area of triangle $ABC$?\hfill(PRMO 2014)
    \item Let $XOY$ be a triangle with $\angle XOY = 90\degree$. Let $M$ and $N$ be the midpoints of legs $OX$ and $OY$, respectively. Suppose that $XN = 19$ and $YM = 22$. What is $XY$?

	    \hfill(PRMO 2014)
\item In $\triangle ABC$, we have $AC = BC = 7$ and $AB = 2$. Suppose that $D$ is a point on line $AB$ such that $B$ lies between $A$ and $D$ and $CD = 8$. What is the length of the segment $BD$?\hfill(PRMO 2012)
\item In rectangle $ABCD$, $AB = 5$ and $BC = 3$. Points $F$ and $G$ are on line segment $CD$ so that $DF = 1$ and $GC = 2$. Lines $AF$ and $BG$ intersect at $E$. What is the area of $\triangle ABE$?\hfill(PRMO 2012)
\item A triangle with perimeter 7 has integer side lengths. What is the maximum possible area of such a triangle?\hfill(PRMO 2012)
\item $ABCD$ is a square and $AB$ = 1. Equilateral triangles $AYB$ and $CXD$ are drawn such that $X$ and $Y$ are inside the square. What is the length of $XY$?\hfill(PRMO 2012)
    \item A $ 2 \times 3 $ rectangle and a $ 3 \times 4 $ rectangle are contained within a square without overlapping at any interior point, and the sides of the square are parallel to the sides of the two given rectangles. What is the smallest possible area of the square? 

	    \hfill(PRMO 2015)

    \item What is the greatest possible perimeter of a right-angled triangle with integer side lengths if one of the sides has length 12? \hfill(PRMO 2015)



\item In the acute-angled triangle $ABC$, let $D$ be the foot of the altitude from $A$, and $E$ be the midpoint of $BC$. Let $F$ be the midpoint of $AC$. Suppose $ \angle BAE = 40\degree $. If $ \angle DAE = \angle DFE $, what is the magnitude of $ \angle ADF $ in degrees?
	\hfill(PRMO 2015)
	\item In an equilateral triangle of side length $6$, pegs are placed at the vertices and also evenly along each side at a distance of $1$ from each other. Four distinct pegs are chosen from the $15$ interior pegs on the sides (that is, the chosen ones are not vertices of the triangle) and each peg is joined to the respective opposite vertex by a line segment. If $N$ denotes the number of ways we can choose the pegs such that the drawn line segments divide the interior of the triangle into exactly nine regions, find the sum of the squares of the digits of $N$.\hfill(IOQM 2015)		
	\item In a triangle $ABC$, let $E$ be the midpoint of $AC$ and $F$ be the midpoint of $AB$. The medians $BE$ and $CF$ intersect at $G$. Let $Y$ and $Z$ be the midpoints of $BE$ and $CF$, respectively. If the area of triangle $ABC$ is 480, find the area of triangle $GYZ$.

		\hfill(IOQM 2015)
    \item Let $X$ be the set of all even positive integers $n$ such that the measure of the angle of some regular polygon is $n$ degrees. Find the number of elements in $X$.

	    \hfill(IOQM 2015)
    \item Let $ABC$ be a triangle in the $xy$-plane, where $B$ is at the origin $\brak{0, 0}$. Let $BC$ be produced to $D$ such that $BC : CD = 1 : 1$, $CA$ be produced to $E$ such that $CA : AE = 1 : 2$, and $AB$ be produced to $F$ such that $AB : BF = 1 : 3$. Let $G\brak{32, 24}$ be the centroid of triangle $ABC$ and $K$ be the centroid of triangle $DEF$. Find the length $GK$.\hfill(IOQM 2015)
    \item A trapezium in the plane is a quadrilateral in which a pair of opposite sides are parallel. A trapezium is said to be non-degenerate if it has positive area. Find the number of mutually non-congruent, non-degenerate trapeziums whose sides are four distinct integers from the set $\cbrak{5, 6, 7, 8, 9, 10}$.\hfill(IOQM 2015)
    
\item Consider the convex quadrilateral $ABCD$. The point $P$ is the interior of $ABCD$. The following ratio equalities hold
\begin{align*}
\angle PAD: \angle PBA: \angle DPA =1:2:3 = \angle CBP: \angle BAP: \angle BPC.
\end{align*} 
prove
 that the following three lines meet in a point: the internal bisectors 
of angles $\angle ADP$ and $\angle PCB$ and the perpendicular bisector 
of segment $AB$.
\hfill(IMO 2020)
\item Three points $ X, Y, Z $ are on a straight line such that $ XY = 10 $ and $ XZ = 3 $. What is the product of all possible values of $ YZ $?\hfill(PRMO 2013)

\item Let $ AD $ and $ BC $ be the parallel sides of a trapezium $ ABCD $. Let $ P $ and $ Q $ be the midpoints of the diagonals $ AC $ and $ BD $. If $ AD = 16 $ and $ BC = 20 $, what is the length of $ PQ $?\hfill(PRMO 2013)

\item Let $ ABC $ be an equilateral triangle. Let $ P $ and $ S $ be points on $ AB $ and $ AC $, respectively, and let $ Q $ and $ R $ be points on $ BC $ such that $ PQRS $ is a rectangle. If $ PQ = \sqrt{3} PS $ and the area of $ PQRS $ is $ \frac{28}{3} $, what is the length of $ PC $?\hfill(PRMO 2013)

\item Let $ A_1, B_1, C_1, D_1 $ be the midpoints of the sides of a convex quadrilateral $ ABCD $ and let $ A_2, B_2, C_2, D_2 $ be the midpoints of the sides of the quadrilateral $ A_1B_1C_1D_1 $. If $ A_2B_2C_2D_2 $ is a rectangle with sides 4 and 6, then what is the product of the lengths of the diagonals of $ ABCD $?\hfill(PRMO 2013)


\item In a triangle $ ABC $ with $ \angle BCA = 90\degree $, the perpendicular bisector of $ AB $ intersects segments $ AB $ and $ AC $ at $ X $ and $ Y $, respectively. If the ratio of the area of quadrilateral $ BXYC $ to the area of triangle $ ABC $ is 13:18 and $ BC = 12 $, then what is the length of $ AC $?\hfill(PRMO 2013)
\item $A$ convex hexagon has the property that for any pair of opposite sides the distance between their midpoints is $\frac{\sqrt{3}}{2}$ times the sum of their lengths Show that all the hexagon's angles are equal.\hfill(IMO 2003)
\item In a triangle $ABC$, let $AP$ bisect $\angle B AC$, with $P$ on $BC$, and let $BQ$ bisect $\angle A BC$, with $Q$ on $CA$. It is known that $\angle BAC= 60\degree$ and that $AB+BP=AQ+QB$. What are the possible angles of triangle $ABC$?\hfill(IMO 2001)
\item Let $d$ be the sum of the lengths of all the diagonals of a plane convex polygon with $n$ vertices $\brak{n>3}$, and let $p$ be its perimeter. Prove that\begin{align*}                                    \ln -3<\frac{2d}{p}<\sbrak{\frac{n}{2}}\sbrak{\frac{n+1}{2}}-2,\end{align*}
		Where $\sbrak{x}$ denotes the greatest integer not exceeding $x$.  \hfill(IMO 1984)
\item $P$ is a point inside a given triangle $ABC$. $D, E, F$ are the feet of the perpendiculars from $P$ to the lines $BC, CA, AB$ respectively. Find all $P$ for which $$\frac{BC}{PD}+\frac{CA}{PE}+\frac{AB}{PF}$$ is least. \hfill(IMO  1981)
 \item The diagonals $AC$ and $CE$ of the regular hexagon $ABCDEF$ are divided by the inner points $M$ and $N$, respectively, so that \begin{align*} \frac{AM}{AC}=\frac{CN}{CE}=r.
                   \end{align*}
 Determine $r$ if $B, M$ and $N$ are collinear. \hfill(IMO  1982)
    \item Let $A$, $B$ be adjacent vertices of a regular $n$-gon $\brak{n\leq5}$ in the plane having center at $O$. A triangle $XYZ$, which is congruent to and initially coincides with $OAB$, moves in the plane in such a way that $Y$ and $Z$ each trace out the whole boundary of the polygon, $X$ remaining inside the polygon. Find the locus of $X$.\hfill(IMO  1986)

\item $ABC$ is a triangle right-angled at $A$, and $D$ is the foot of the altitude from $A$. The straight line joining the incenters of the triangles $ABD$, $ACD$ intersects the sides $AB$, $AC$ at the points $K$, $L$ respectively. $S$ and $T$ denote the areas of the triangles $ABC$ and $AKL$ respectively. Show that $S\geq 2T$.\hfill(IMO  1988)
	\item Let $ABCD$ be a convex quadrilateral such that the sides ${AB, AD, BC}$ satisfy $AB= AD + BC$. There exists a point $P$ inside the quadrilateral at a distance $h$ from the line $CD$ such that $AP= h+ AD$ and $BP= h + BC$. Show that \begin{align*}
	\frac{1}{\sqrt{h}}\geq\frac{1}{\sqrt{AD}}+\frac{1}{\sqrt{BC}}\end{align*}. \hfill(IMO  1989)
\item Prove that there exists a convex $1990$-gon with the following     two properties
\begin{enumerate}
\item All angles are equal.
\item The lengths of the 1990 sides are the numbers $1^2, 2^2, 3^2,\dots 1990^2$ in some order.\hfill(IMO  1990)
\end{enumerate}
%
\item Let $ABC$ be a triangle and $P$ an interior point of $ABC$.     Show that at least one of the angles $\angle{PAB}, \angle{PBC}, \angle{PCA}$ is less than or equal to $30\degree$.\hfill(IMO  1991)
%
\item Equilateral triangles $ABK$, $BCL$, $CDM$, $DAN$ are constructed inside the square $ABCD$. Prove that the midpoints of the four segments $KL$, $LM$, $MN$, $NK$ and the midpoints of the eight segments $AKBK$, $BL$, $CL$, $CM$, $DM$, $DN$, $AN$ are the twelve vertices of a regular dodecagon.\hfill(IMO  1977).
\item A triangle $A_1A_2A_3$ and a point $P_0 $ are given in the plane. We define $A_s
    =A_s-3$ for all $s\geq4$. We construct a set of points $P_1$, $P_2$, $P_3$ \dots, such that $P_{k+1}$ is the image of $P_k$ under a rotation with center $A_{k+1}$ through angle $120\degree$ clockwise for $\brak{k=0,1,2,3\dots}$. Prove that if $P_{1986}$=$P_0$, then the triangle $A_1A_2A_3$ is equilateral.\hfill(IMO  1986)
%
	\item Six points are chosen on the sides of an equilateral triangle $ABC$:
     $A_1$,$A_2$ on $BC$,$B_1$,$B_2$ on $CA$ and $C_1$,$C_2$ on $AB$, such that they are the vertices of a convex hexagon $A_1A_2$ $B_1B_2$ $C_1C_2$ with equal side lengths. Prove that the line $A_1B_2$,$B_1C_2$ and $C_1A_2$ are concurrent.\hfill(IMO  2005)
\item Let $P$ be a regular 2006-gon. A diagonal of $P$ is called good if its endpoints divide the boundary of $P$ into two parts, cach composed of an odd mumber of sides of P. The sides of $P$ are also called good. Suppose $P$ has been dissected into triangles by 2003 diagonals, no two of which have a common point in the interior of $P$. Find the maximum number  of isosceles triangles having two good sides that could appear in such a configuration. \hfill(IMO  2006)
\item Assign to each side $b$ of a convex polygon $P$ the maximum area of a triangle that has $b$ as a side and is contained in $P$. Show that the sum of the areas assigned to the sides of $P$ is at least twice the area of $P$.\hfill(IMO  2006)
\item Let $ABCDEF$ be a convex hexagon with $AB=BC=CD$ and $DE=EF=FA$, such that $\angle{BCD}=\angle{EFA}=\frac{\pi}{3}$. Suppose $G$ and $H$ are points in the interior of the hexagon such that $\angle{AGB}=\angle{DHE}=\frac{2\pi}{3}$. Prove that $AG+GB+GH+DH+HE\geq CF$.

	\hfill (IMO  1995)
 \item Triangle $BCF$ has a right angle at $B$. Let $A$ be the point on line $CF$ such that $FA=FB$ and $F$ lies between $A$ and $C$. Point $D$ is chosen such that $DA = DC$ and $AC$ is the bisector of $\angle DAB$. Point $E$ is chosen such that $EA= ED$ and $AD$ is the bisector of $\angle EAC$. Let $M$ be the midpoint of $CF$. Let $X$ be the point such that $AMXE$ is a parallelogram (where $AM \parallel EX$ and $AE \parallel MX)$. Prove that lines $BD, FX$, and $ME$ are concurrent.\hfill (IMO  2016)
\item $A$ convex quadrilateral $ABCD$ satisfies \begin{align*}AB.CD=BC.DA.\end{align*} Point $X$ lies inside $ABCD$ so that \begin{align*}\angle XAB=\angle XCD \text{ and } \angle XBC=\angle XDA.    \end{align*} Prove that\begin{align*}\angle BXA+\angle DXC=180\degree.\end{align*}\hfill (IMO  2018)
\item For three points $P, Q, R$ in the plane, we define $m(PQR)$ as the minimum length of the three altitudes of $\triangle PQR$. (If the points are collinear, we set $m(PQR) = 0$.)                                                                           
  Prove that for points $A, B, C, X$ in the plane,
 \hfill(IMO  1993)
\begin{align*}
                                                     m(ABC) \leq m(ABX) + m(AXC) + m(XBC).
\end{align*}
\item $ABC$ is an isosceles triangle with $AB = AC$. Suppose that  
$M$ is the midpoint of $BC$ and $O$ is the point on the line $AM$ such that $OB$ is perpendicular to $AB$.
\hfill(IMO  1994)
\begin{enumerate}
\item $Q$ is an arbitrary point on the segment $BC$ different from $B$ and $C$;                           
\item $E$ lies on the line $AB$ and $F$ lies on the line $AC$ such that $E$, $Q$, $F$ are distinct and collinear.
 
		 Prove that $OQ$ is perpendicular to $EF$ if and only if $QE=QF$.    
\end{enumerate}
%
\item Four real constants $a, b, A, B$ are given, and \begin{align*}
f\brak{\theta} = 1 - a\cos\theta - b \sin \theta     - A \cos 2\theta - B \sin 2\theta  
\end{align*}. Prove that if 
\begin{align*}f\brak{\theta} \ge 0 
	\end{align*} for all real $\theta$, then
(IMO  1977)
\begin{align*} a^{2} + b^{2} \leq 2 \text{ and } A^{2} + B^{2} \leq  1 
\end{align*}\hfill
\end{enumerate}
