\item A moving boat is observed from the top of a $150m$ high cliff moving away from the cliff. The angle of depression of the boat changes from $60\degree$ to $45\degree$ in $2$ minutes. Find the speed of the boat in m/min.

\hfill\brak{10, 2019}\item There are two poles, one each on either bank of a river just opposite to each other. One pole is $60m$ high. From the top of this pole, the angle of depression of the top and foot of the other pole are $30\degree$ and $60\degree$respectively. Find the width of the river and height of the other pole.

\hfill\brak{10, 2019}\item Two poles of equal heights are standing opposite to each other on either side of the road which is $80 m$ wide. From a point $P$ between them on the road, the angle of elevation of the top of a pole is $60\degree$ and the angle of depression from the top of the other pole of point $P$ is $30\degree$. Find the heights of the poles and the distance of the point $P$ from the poles.

\hfill\brak{10, 2019}\item Amit, standing on a horizontal plane, finds a bird flying at a distance of $200 m$ from him at an elevation of $30\degree$. Deepak standing on the roof of a $50 m$ high building, finds the angle of elevation of the same bird to be $45\degree$. Amit and Deepak are on opposite sides of the bird. Find the distance of the bird from Deepak.

\hfill\brak{10, 2019}\item From a point $P$ on the ground, the angle of elevation of the top of a tower is $30\degree$ and that of the top of the flag-staff fixed on the top of the tower is $\sqrt{5}$. If the length of the flag-staff is $5 m$, find the height of the tower. (Use $\sqrt{3}= 1.732$).


\hfill\brak{10, 2019}\item The shadow of a tower standing on a level ground is found to be $40 m$ longer when the Sun's altitude is $30\degree$ than when it was $60\degree$. Find the height of the tower. $(Given \sqrt{3} = 1.732)$

\hfill\brak{10, 2019}\item A man in a boat rowing away from a light house $100m$  high takes $2$ minutes to change the angle of elevation of the top of the light house from $60\degree$ to $30\degree$. Find the speed of the boat in metres per minute. [Use $\sqrt{3}=1.732$]
\hfill\brak{10, 2019}\item Two poles of equal heights are standing opposite each other on either side of the road, which is $80 m$  wide. From a point between them on the road, the angles of elevation of the top of the poles are $60\degree$ to $30\degree$ respectively. Find the height of the poles and the distances of the point from the poles.
\hfill\brak{10, 2019}
