\begin{enumerate}
   \item A natural number $k$ is such that $k^2 < 2014 , (k+1)^2$. What is the largest prime factor of $k$?\hfill(PRERMO 2014)
   \item The first term of a sequence is $2014$. Each succeeding term is the sum of the cubes of the digits of the previous term. What is the $2014^{th}$ term of the sequence?\hfill(PRERMO 2014)
   \item What is the smallest possible natural number $n$ for which the equation $x^2 - nx + 2014 = 0$ has integer roots?\hfill(PRERMO 2014)
   \item If $x^{\brak{x^4}} = 4$, what is the value of $x^{\brak{x^2}} + x^{\brak{x^8}}$?\hfill(PRERMO 2014)
   \item Let $S$ be a set of real numbers with mean $M$. If the means of the sets $S \cup \{15\}$ and $S \cup \{15, 1\}$ are $M + 2$ and $M + 1$, respectively, then how many elements does $S$ have?
   \item Natural numbers $k, l, p,$ and $q$ are such that $a$ and $b$ are roots of the equation $x^2 - kx + l = 0$ such that $a + \frac{1}{b}$ and $b + \frac{1}{a}.$What is the sum of all possible values of $q$?\hfill(PRERMO 2014)
   \item For natural numbers $x$ and $y$, let $\brak{x, y}$ denote the greatest common divisor of $x$ and $y$. How many pairs of natural numbers $x$ and $y$ with $x \leq y$ satisfy the equation $xy = x + y + \brak{x, y}$?\hfill(PRERMO 2014)
   \item For how many natural numbers $n$ between $1$ and $2014$ \brak{both inclusive} is $\frac{8n}{9999 - n}$ an integer?\hfill(PRERMO 2014)
   \item For a natural number $b$, let $N\brak{b}$ denote the number of natural numbers $a$ for which the equation $x^2 + ax + b = 0$ has integer roots. What is the smallest value of $b$ for which $N\brak{b} = 20$?\hfill(PRERMO 2014)
    \item One morning, each member of Manjul's family drank an 8-ounce mixture of coffee and milk. The amounts of coffee and milk varied from cup to cup, but were never zero. Manjul drank $\frac{1}{7}$-th of the total amount of milk and $\frac{2}{17}$-th of the total amount of coffee. How many people are there in Manjul's family?\hfill(PRERMO 2014)
\end{enumerate}
