\begin{enumerate}[label=\thesubsection.\arabic*.,ref=\thesubsection.\theenumi]
\item A ladder is placed against a wall such that its foot is at a distance of 2.5$m$ from the wall and its top reaches a window 6$m$ above the ground. Find the length of the ladder.
\item  A ladder 10$m$ long reaches a window 8$m$ above the ground. Find the distance of the foot of the ladder from base of the wall.
\item  A guy wire attached to a vertical pole of height 18$m$ is 24$m$ long and has a stake attached to the other end. How far from the base of the pole should the stake be driven so that the wire will be taut?
\item  An aeroplane leaves an airport and flies due north at a speed of 1000$km$ per hour. At the same time, another aeroplane leaves the same airport and flies due west at a speed of 1200$km$ per hour. How far apart will be the two planes after $1\frac{1}{2}$ hours?
\item  Two poles of heights 6$m$ and 11$m$ stand on a plane ground. If the distance between the feet of the poles is $12m$, find the distance between their tops.
\item An aircraft is flying at a height of 3400$m$ above the ground. If the angle subtended at a ground observation point by the aircraft positions $10.0s$ apart is 30$\degree$, what is the speed of the aircraft ?
%
\item A statue, 1.6$m$ tall, stands on the top of a pedestal. From a point on the ground, the angle of elevation of the top of the statue is 60$\degree$ and from the same point the angle of elevation of the top of the pedestal is 45$\degree$. Find the height of the pedestal.
\item The angle of elevation of the top of a building from the foot of the tower is 30$\degree$ and the angle of elevation of the top of the tower from the foot of the building is 60$\degree$. If the tower is 50$m$ high, find the height of the building.
\item Two poles of equal heights are standing opposite each other on either side of the road, which is 80$m$ wide. From a point between them on the road, the angles of elevation of the top of the poles are 60$\degree$ and 30$\degree$, respectively. Find the height of the poles and the distances of the point from the poles.
\item A TV tower stands vertically on a bank of a canal. From a point on the other bank directly opposite the tower, the angle of elevation of the top of the tower is 60$\degree$. From another point 20$m$ away from this point on the line joing this point to the foot of the tower, the angle of elevation of the top of the tower is 30$\degree$. Find the height of the tower and the width of the canal.
\item From the top of a 7$m$ high building, the angle of elevation of the top of a cable tower is 60$\degree$ and the angle of depression of its foot is 45$\degree$. Determine the height of the tower.
\item As observed from the top of a 75$m$ high lighthouse from the sea-level, the angles of depression of two ships are 30$\degree$ and 45$\degree$. If one ship is exactly behind the other on the same side of the lighthouse, find the distance between the two ships.
\item A 1.2$m$ tall girl spots a balloon moving with the wind in a horizontal line at a height of 88.2$m$ from the ground. The angle of elevation of the balloon from the eyes of the girl at any instant is 60$\degree$. After some time, the angle of elevation reduces to 30$\degree$. Find the distance travelled by the balloon during the interval.
\item A straight highway leads to the foot of a tower. A man standing at the top of the tower observes a car at an angle of depression of 30$\degree$, which is approaching the foot of the tower with a uniform speed. Six seconds later, the angle of depression of the car is found to be 60$\degree$. Find the time taken by the car to reach the foot of the tower from this point.
\item The angles of elevation of the top of a tower from two points at a distance of 4$m$ and 9$m$ from the base of the tower and in the same straight line with it are complementary. Prove that the height of the tower is $6m$.
\item A girl of height 90$cm$ is walking away from the base of a lamp-post at a speed of 1.2 $m/s$. If the lamp is 3.6$m$ above the ground, find the length of her shadow after 4 seconds.
\item  Nazima is fly fishing in a stream. The tip of her fishing rod is 1.8$m$ above the surface of the water and the fly at the end of the string rests on the water 3.6$m$ away and 2.4$m$ from a point directly under the tip of the rod. Assuming that her string (from the tip of her rod to the fly) is taut, how much string does she have out? If she pulls in the string at the rate of 5$cm$ per second, what will be the horizontal distance of the fly from her after 12 seconds?
%
\item  A vertical pole of length 6$m$ casts a shadow 4$m$ long on the ground and at the same time a tower casts a shadow 28$m$ long. Find the height of the tower.
\item A circus artist is climbing a $20m$ long rope, which is tightly stretched and tied from the top of a vertical pole to the ground.  Find the height of the pole, if the angle made by the rope with the ground level is 30$\degree$.
%
\item A tree breaks due to storm and the broken part bends so that the top of the tree touches the ground making an angle of 30$\degree$ with it.  The distance between the foot of the tree to the point where the top touches the ground is $8m$.  Find the height of the tree.
%
\item A contractor plans to install two slides for the children to play in a park.  For the children below the age of 5 years, she prefers to have a slide whose top is at a height of 1.$5m$, and is inclined at an angle of 30$\degree$  to the ground, whereas for elder children she wants to have a steep slide at a height of $3m$, and inclined at an angle of 60$\degree$ to the ground.  What should be the length of the slide in each case?
%
\item The angle of elevation of the top of a tower from a point on the ground, which is $30m$ away from the foot of the tower, is 30$\degree$.  Find the height of the tower.
%
\item A kite is flying at a height of $60m$ above the ground.  The string attached to the kite is temporarily tied to a point on the ground.  The inclination of the string with the ground is $60\degree$.  Find the length of the string, assuming that there is no slack in the string.
%
\item A $1.5m$ tall boy is standing at some distance from a $30m$ tall building.  The angle of elevation from his eyes to the top of the building increases from 30$\degree$
 to 60$\degree $ as he walks towards the building.  Find the distance he walked towards the building.

\item From a point on the ground, the angles of elevation of the bottom and the top of a transmission tower fixed at the top of a 20$m$ high building are 45$\degree$ and 60$\degree$ respectively. Find the height of the tower.

\item A girl walks $4km$ west, then she walks $3km$ in a direction $30\degree$ east of north and stops.  Determine the girl's displacement from her initial point of departure.
\item The angles of depression of the top and the bottom of an $8m$ tall building from the top of a multi-storeyed building are 30$\degree$ and 45$\degree$ respectively.  Find the height of the multi-storeyed building and the distance between the two buildings.
\item A tower stands vertically on the ground.  From a point on the ground, which is 1$5m$ away from the foot of the tower, the angle of elevation of the top of the tower is found to be 60$\degree$.  Find the height of the tower.
\item An electrician has to repair an electric fault pole of height $5m$.  She needs to reach a point $1.3m$ below the top of the pole to undertake the repair work.  What should be the length of the ladder that she should use which, when inclined at an angle of 60$\degree$ to the horizontal, would enable her to reach the required position?  Also, how far from the foot of the pole should she place the foot of the ladder?
\item An observer $1.5m$ tall is 28.$5m$ away from a chimney.  The angle of elevation of the top of the chimney from her eyes is 45$\degree$.  What is the height of the chimney?
\item From a point ${P}$ on the ground the angle of elevation of the top of a 10m tall building is 30$\degree$.  A flag is hoisted at the top of the building and the angle of elevation of the top of the flagstaff from ${P}$ is $45\degree$.  Find the length of the flagstaff and the distance of the building from the point ${P}$.
\item The shadow of a tower standing on a level ground is found to be $40m$ longer when the Sun's altitude is 30$\degree$ than when it is $60\degree$.  Find the height of the tower.
\end{enumerate}
